Forward Modeling Galaxy Size in a Cosmological Context

### 2017-10-05 paper/galsize_paper.tex
Updated acknowledgements

APH thanks John Baker for the {\em Toejam \& Earl} soundtrack. Thanks also to Frank van den Bosch, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work.

>>>>

APH thanks John Baker for the {\em Toejam \& Earl} soundtrack. Thanks also to Frank van den Bosch, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, and to Faustin Carter and Sebastian Bocquet for sharing their python expertise.
